%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv}% Default font size, values from 8-12pt are recommended


%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.55\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Szymon}}}}} % First name

	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Kaszuba-Gałka}}}}} % Last name


	\vspace{5pt}


	{\huge} % Career or current job title

\end{minipage}
\begin{minipage}[t]{0.35\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages


	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Łódź, Polska}\\
	\icon{Phone}{12}{+48 794 03 03 63}\\
	\icon{At}{12}{\href{mailto:szymonkaszubagalka.innovio@gmail.com}{szymonkaszubagalka.innovio@gmail.com}}\\
	\icon{Github}{12}{\href{https://github.com/Szymonexis}{Szymonexis}}\\
	\icon{Linkedin}{12}{\href{https://www.linkedin.com/in/szymon-kaszuba-gałka/}{Szymon Kaszuba-Gałka}}\\
\end{minipage}


\vspace{0.3cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------


\begin{minipage}[t]{0.45\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip}
	\cvsect{Professional Summary}

	Senior Fullstack Developer with 3+ years of experience building scalable web applications and AI-driven solutions. Proven expertise in Angular, TypeScript, and cloud technologies. Master's candidate in Computer Science with a track record of delivering enterprise-grade solutions for global brands. Specialized in fullstack development, microservices architecture, and test automation.
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}
	\vspace{-\baselineskip}
	\cvsect{Skills}
	\begin{barchart}{3}
		\baritem{Angular}{100}
		\baritem{Typescript/Javascript}{100}
		\baritem{Nest.js}{90}
		\baritem{AWS/GCP}{80}
		\baritem{Docker/Kubernetes}{80}
		\baritem{React}{75}
		\baritem{Python}{70}
		\baritem{React-native}{70}
		\baritem{Golang}{70}
		\baritem{Java}{70}
		\baritem{C-sharp}{60}
	\end{barchart}
\end{minipage}
\vspace{1.0cm}

\begin{minipage}[t]{0.45\textwidth}
	\vspace{-\baselineskip}
	\cvsect{Currently using}

	Typescript, Golang, Python, Angular, Nest.js, AWS/GCP, Docker/Kubernetes,
	Websockets, Pub-Sub model, Github Actions, NgRx, Redux, Signals, Axios,
	PostgreSQL, WebComponents, AWS, Jest, Supertest
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}
	\vspace{-\baselineskip}
	\cvsect{Used in the past}

	Cypress and Jester (E2E testing), D3, Oracle ECharts, C-Sharp, Golang, React-native, React, Tauri, Ionic (with Capacitor), Java (8 and 12), Python
\end{minipage}
\vspace{1.0cm}

% \begin{center}
% 	    \bubbles{5/Office, 2/Linux}
% \end{center}
%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\cvsect{Experience}

\begin{entrylist}
	\entry
	{10.2025 - Now}
	{University Lecturer}
	{Vizja University Warsaw}
	{Instructor for "Paradigms and Programming Languages" course, teaching Java, Python, and JavaScript fundamentals. Delivering weekend and evening lectures and practical exercise sessions for multiple student groups, emphasizing core programming concepts and language-specific best practices.}
	\entry
	{10.2024 - Now}
	{Senior Fullstack Developer}
	{Digibate ApS}
	{Leading development of an AI-powered marketing platform for SMBs using Angular, OpenAI API, Nest.js, and event-driven architecture. Spearheaded comprehensive backend and frontend refactoring to improve stability and performance. Key achievements: migrated database from MySQL to PostgreSQL, implemented custom OAuth 2.1 authentication, developed Model Context Protocol (MCP) server, and established comprehensive E2E testing infrastructure using Cypress, Jest, and Supertest.}
	\entry
	{06.2022 - 11.2024}
	{Mid Frontend Developer}
	{WPP plc.}
	{Developed and maintained Angular applications (versions 7-18) for market analysis platforms serving enterprise clients including BMW, Coca-Cola, Amazon, and L'Oréal. Built standalone and microfrontend architectures. Led E2E testing initiatives including training programs and complete test pipeline implementation using Cypress for two major projects.}
	\entry
	{03.2022 - 11.2024}
	{Junior Frontend Developer / Mid Fullstack Developer}
	{Digimonkeys.com sp. z o.o.}
	{Developed "Dr. HairCare" - an algorithmic hair care platform for personalized treatment recommendations. Built cross-platform solutions including a Raspberry Pi-based automated response system with integrated mobile application for streamlined user management.}
	\entry
	{08.2021 - 03.2022}
	{Intern Backend Developer}
	{mBank S.A.}
	{Developed and maintained Java-based credit system infrastructure for one of Poland's largest banks. Utilized Python for data analysis and system optimization. Enhanced system reliability and performance through code improvements and bug fixes.}
	\entry
	{06.2017 - 04.2021}
	{Senior Service Agent}
	{Fujitsu Technology Solutions}
	{Provided first-line IT support for UK and Nordic enterprise users. Managed tickets through ServiceNow, administered Oracle databases and Active Directory, and delivered technical solutions using internal support tools.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
	{2022 - 2025}
	{Computer Science [Master's]}
	{University of Łódź}
	{Master's degree in Computer Science at the Faculty of Mathematics and Computer Science. Currently completing thesis on advanced software engineering topics.}
	\entry
	{2019 - 2022}
	{Computer Science [Bachelor's]}
	{University of Łódź}
	{Bachelor's degree in Computer Science, specializing in Networks and Data Processing. Thesis: "WebSocket Applications in Audio and Video Streaming."}
\end{entrylist}


\cvsect{Soft skills}
\begin{itemize}
	\item Strong leadership capabilities with a primary focus on delivering high-quality, responsive, and maintainable software solutions
	\item Quick learner with excellent decision-making abilities and analytical thinking
	\item Effective team collaborator with proven ability to work independently when required
	\item Excellent communicator and active listener, facilitating productive cross-functional collaboration
	\item Analytical problem solver with systematic approach to complex technical challenges
	\item Strong planning and organizational skills with ability to deliver under pressure
\end{itemize}
\vspace{0.5cm}
%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}

	\textbf{Polish} - Native \\
	\textbf{English} - C1
\end{minipage}
\hfill
\begin{minipage}[t]{0.7\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Hobbies}

	Software development enthusiast with interests in mathematics, gaming (video games, board games, and tabletop RPGs), automotive technology, and cinema. Avid film enthusiast with particular appreciation for classics including "Scarface," "The Martian," "Vanilla Sky," and "Mulholland Drive."
\end{minipage}
\vspace{1.5cm}

%----------------------------------------------------------------------------------------
\noindent\rule{8cm}{0.4pt}

I consent to the processing of my personal data for the purposes of the recruitment process in accordance with Regulation (EU) 2016/679 of the European Parliament and of the Council of 27 April 2016 on the protection of individuals with regard to the processing of personal data and on the free movement of such and the repeal of Directive 95/46/EC (GDPR).
\end{document}
